---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Open+Sans:ital,wght@0,300..800;1,300..800&display=swap');

body {
  background: linear-gradient(135deg, #f5f7fa, #88d9e6);
  font-family: 'Open Sans';
  font-size: 16px;
  line-height: 1.6;
  color: #222;
  padding: 20px;
}

h2 {
    color: #1a73e8;
    background-color: rgba(255, 255, 255, 0.6);
    font-weight: bold;
    border-bottom: 2px solid #1a73e8;
    padding-bottom: 5px;
}

img {
    border: 3px solid #1a73e8;
    border-radius: 10px;
    padding: 5px;
    max-width: 60%;
    height: auto;
    display: block;
    margin: 10px auto;
}
```

## My Dynamic Report - An analysis of 21 days of my sleep data
<p>
This report analyses my sleep quality/duration over 21 days in March, 2025. <br>
The following factors were recorded:<br>
<ul>
<li>Sleep quality rating (on a scale of 1 - 10)</li>
<li>Pre-bedtime app usage + content category</li>
</ul>
</p>

```{r}
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQtgCBkmh_SoecUmPg2gGAYAntfvS-G5efNBRFkoMVQVDfzv6_q0HgEqvtT0dTV5IHtyVV9Xr4bi1Ja/pub?gid=227145503&single=true&output=csv"

logged_data <- read_csv(csv_file)

latest_data <- logged_data %>% 
  rename(last_app_used = 2,
         type_of_content = 3,
         date = 4,
         daily_screen_time = 5,
         bedtime = 6,
         sleep_quality = 7,
         sleep_duration = 8)

#Part D
# 1. average sleep quality: (summary value)
avg_sleep_quality <- round(sum(latest_data$sleep_quality) / nrow(latest_data), 1)

# 3. most used app before bed: (summary value)
all_apps <- latest_data$last_app_used
most_used_app <- max(all_apps)

# good sleep nights
good_sleep_nights <- sum(latest_data$sleep_quality >= 8)

# bad sleep nights
bad_sleep_nights <- sum(latest_data$sleep_quality <= 4)
```

## Average Sleep Quality
<p> Over the 21 days where I recorded the quality of my sleep, my average sleep quality came to **`r avg_sleep_quality `** out of 10. This was actually a bit surprising to me, as I consider myself someone who has *very* poor sleeping habits. <br>
In hindsight, my self-rating could have actually been heavily impacted on the amount of caffeine I consumed after I woke up. So maybe next time, I need to ensure that I rate my sleep right after I wake up, or see if the quality can be 'objectified' by 'how many cans of coffee I drank the next day' instead.</p>

## Most used app before sleeping
<p> The next thing I looked at was the apps that I used right before sleeping. I'm someone who struggles to go to sleep, so I've slowly developed the habit of *needing* to listen to or watch something to help me fall asleep. <br>
Over the 6 or so apps that I commonly use, the most common app was **`r most_used_app`**. 
<br>
Maybe it's time for me to consider deleting **`r most_used_app`**.....
<br>
</p>

## Sleep Quality Plot
<p>Now that I've seen the average value of my sleep quality (**`r avg_sleep_quality`**), I wanted to see a visual breakdown of all my ratings. While the average gives me a good understanding, the distribution of data can show me more about the consistency of my sleep quality.<br>

```{r fig.width = 8, fig.height = 4}
# 6. plot 3 - sleep quality over the 21 days (plot/bar chart)
ggplot(data = latest_data) +
  geom_bar(aes(x = sleep_quality), fill = "navy") +
  labs(
    title = "Sleep Quality Satisfaction",
    subtitle = "Recorded over 21 days in March 2025 using a scale of 1 to 10, where 10 is the most satisfactory",
    x = "Sleep Quality Reflection (scale of 1 to 10)",
    y = "Frequency (Over 21 days)") +
  scale_x_continuous(breaks=seq(1,10,by=1), limits=c(0.5,10.5))
```
<p>
From the plot, I can see that I had **`r good_sleep_nights`** nights of excellent sleep quality, where I rated it higher or equal to an 8. There were also **`r bad_sleep_nights`** nights where I did not sleep very well. My lowest rated sleep was at **`r min(latest_data$sleep_quality)`** out of 10, and my highest rating was **`r max(latest_data$sleep_quality)`** out of 10.
</p>

## Type of Content Consumed
<p>
Now that I have a thorough understanding of my sleep quality over the 21 days, I can start looking at its correlation to the type of content I consumed before sleeping.<br>
To visualise this, I plotted all the categories of content I looked at before sleeping. I decided to use content type instead of app because it would give me a clearer breakdown of how engaging or stimulating the content was. 
</p>
```{r fig.width = 8, fig.height = 4}
# 4. plot 1 - types of content consumed before bed (plot/bar chart)
ggplot(data = latest_data) +
  geom_bar(aes(x = type_of_content), fill = "navy") +
  labs(
    title = "Type of Content Consumed Before Sleeping",
    subtitle = "Only the LAST content consumed before sleeping is counted",
    x = "Content Type",
    y = "Frequency (Over 21 days)")
```

